### 2018-02-05 pkg/mapmisc/inst/extdoc/world.Rmd
hopefully all the caching stuff works now
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1903 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r theHeader, echo=FALSE}
knitr::knit_hooks$set(plot=knitr::hook_plot_tex) 
Pmisc::markdownHeader(
  title="Maps of the world", 		
  author='Patrick Brown',
  geometry='margin=1in'
)

```{r worldCrs, tidy=TRUE, warning=FALSE}
require('mapmisc', quietly=TRUE) 
options(mapmiscCachePath = system.file('extdata', package='mapmisc'))

>>>>

```{r theHeader, echo=FALSE}
knitr::knit_hooks$set(plot=knitr::hook_plot_tex) 
Pmisc::markdownHeader(
  title="Maps of the world", 		
  author='Patrick Brown',
  geometry='margin=1in'
)
```

```{r worldCrs, tidy=TRUE, warning=FALSE}
require('mapmisc', quietly=TRUE)
